Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2021-05-14 minimax.tex
Pess strat

Another interesting measure is the average number of questions asked to each participant before reaching zero regret. The results for various sizes are displayed in the last two columns of \cref{tab:questions}.

It is important to mention that we stop our computation at $1000$ questions, the empty cells in \cref{tab:questions} indicate, thus, that the Pessimistic strategy applied to that dataset did not reach zero regret in $1000$ questions.
\commentOC{Need to drop the explanation in Table 2 as this is now explained in the text; change qcMMR=n/10 to qcMMR=0, and add in the text the explanation about qxMMR=; change hyphens to blanks in the table,= I suppose.}
%For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
\vspace{-0.6cm}
\begin{table}
	\caption{Questions asked by Pessimistic strategy on several datasets. The column $q_{c \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{c \scriptscriptstyle{\MMR} = 0}$) indicates the avg number of questions asked to the chair to reach a threshold regret of $\frac{n}{10}$ (zero regret). The column $q_{v \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{v \scriptscriptstyle{\MMR} = 0}$) represents the avg of the quartiles of the questions asked to the voters to reach $\frac{n}{10}$ regret (zero regret).}
	\label{tab:questions}
	\begin{tabular}{cccS[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2] S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]} S[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2]S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]}}
		\toprule
		{dataset} & m & n &{$q_{c \scriptscriptstyle{\MMR} ≤ n/10}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c \scriptscriptstyle{\MMR} = 0}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} = 0}$} \\
		\midrule
		m5n20 & 5&20&0.0&0.0&[4.3 &4.95 & 5.84 &5.25&9.59&[ \ 5.36 & 6.15 & 7.21\\
		m10n20&10&20&0.0&0.0&[13.85 & 16.1& 18.41&31.95&26.62&[19.66 & 21.78 & 24.7\\
		m11n30&11&30&0.0&0.0&[16.55&19.0&22.26&45.15&40.14&[23.07&25.7&28.89\\
		tshirts&11&30&0.0&0.0&[12.92 & 16.17 &19.3\\
		courses&9&146&0.0&0.0&[6.35 &7.0 &7.0&0.0&0.0&[6.8 & 7.0 &7.0\\
		%m9n146&9&146&0&0&[1.94 &8 &9.25&999.3&0.47&0&0&[1.94&8&9.25&999.3&0.47\\
		m14n9&14&9&5.4&9.49&[30.3&33.45&36.65&64.05&40.37&[37.55&40.5&44.3\\
		skate&14&9&0.0&0.0&[11.35&11.8&12.25&0.0&0.0&[11.5&11.9&12.7 \\
		m15n30&15&30&0.0&0.0&[24.95&29.5&33.68 \\

>>>>

Another interesting measure is the average number of questions asked to each participant before reaching zero regret. The results for various sizes are displayed in the last two columns of \cref{tab:questions}. Here, we see that the Pessimistic strategy does choose to question the chair when reaching low enough regret values. The tshirts and m15n30 datasets did not reach zero regret in $1000$ questions.

\commentOC{Need to drop the explanation in Table 2 as this is now explained in the text; change qcMMR=n/10 to qcMMR=0, and add in the text the explanation about qxMMR=; change hyphens to blanks in the table.}
%For example, in the case $m = 10, n = 20$, Pessimistic asks on average $49$ questions to the chair and $18$ questions to each agent (\cref{tab:Numquestions} provides more data).
\vspace{-0.6cm}
\begin{table}
	\caption{Questions asked by Pessimistic strategy on several datasets. The column $q_{c \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{c \scriptscriptstyle{\MMR} = 0}$) indicates the avg number of questions asked to the chair to reach a threshold regret of $\frac{n}{10}$ (zero regret). The column $q_{v \scriptscriptstyle{\MMR} ≤ n/10}$ ($q_{v \scriptscriptstyle{\MMR} = 0}$) represents the avg of the quartiles of the questions asked to the voters to reach $\frac{n}{10}$ regret (zero regret).}
	\label{tab:questions}
	\begin{tabular}{cccS[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2] S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]} S[table-number-alignment = right, table-figures-integer=2]@{ ± }S[table-number-alignment = left, table-figures-integer=2]S[table-figures-integer=3, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ | }S[table-figures-integer=2, table-figures-decimal=1]@{ ]}}
		\toprule
		{dataset} & m & n &{$q_{c \scriptscriptstyle{\MMR} ≤ n/10}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} ≤ n/10}$} & {$q_{c \scriptscriptstyle{\MMR} = 0}$} & {sd} & \multicolumn{3}{c}{$q_{v \scriptscriptstyle{\MMR} = 0}$} \\
		\midrule
		m5n20 & 5&20&0.0&0.0&[4.3 &4.95 & 5.84 &5.25&9.59&[ \ 5.36 & 6.15 & 7.21\\
		m10n20&10&20&0.0&0.0&[13.85 & 16.1& 18.41&31.95&26.62&[19.66 & 21.78 & 24.7\\
		m11n30&11&30&0.0&0.0&[16.55&19.0&22.26&45.15&40.14&[23.07&25.7&28.89\\
		tshirts&11&30&0.0&0.0&[12.92 & 16.17 &19.3\\
		courses&9&146&0.0&0.0&[6.35 &7.0 &7.0&0.0&0.0&[6.8 & 7.0 &7.0\\
		%m9n146&9&146&0&0&[1.94 &8 &9.25&999.3&0.47&0&0&[1.94&8&9.25&999.3&0.47\\
		m14n9&14&9&5.4&9.49&[30.3&33.45&36.65&64.05&40.37&[37.55&40.5&44.3\\
		skate&14&9&0.0&0.0&[11.35&11.8&12.25&0.0&0.0&[11.5&11.9&12.7 \\
		m15n30&15&30&0.0&0.0&[24.95&29.5&33.68 \\
